\documentclass[
  % Babel language, also used to load translations
  english,
  % Use A4 paper size, you can change this to eg. letterpaper if you need
  % the letter format. The normal methods to modify the paper size should
  % be picked up by SDAPS automatically.
  % a4paper, % setting this might break the example scan unfortunately
  % letterpaper
  %
  % If you need it, you can add a custom barcode at the center
  globalid=Flatpak,
  %
  % And the following adds a per sheet barcode at the bottom left
  %print_questionnaire_id,
  %
  % You can choose between twoside and oneside. twoside is the default, and
  % requires the document to be printed and scanned in duplex mode.
  %oneside,
  %
  % With SDAPS 1.1.6 and newer you can choose the mode used when recognizing
  % checkboxes. valid modes are "checkcorrect" (default), "check" and
  % "fill".
  %checkmode=checkcorrect,
  %
  % The following options make sense so that we can get a better feel for the
  % final look.
  pagemark,
  style=qr,
  stamp]{sdapsclassic}

\author{}
\title{GUADEC Workshop Evaluation}


\begin{document}

  \begin{questionnaire}

%    \section{About you}

%    \begin{choicequestion}[cols=4]{Are you a foundation member?}
%      % Hack until this is properly supported somehow.
%      % Multiple answers are possible, but *shrug*
%      \ExplSyntaxOn
%      \sdaps_context_set:n {checkbox={ellipse}}
%      \ExplSyntaxOff
%      \choiceitem{Member}
%      \choiceitem{Not a member}
%      \choiceitem{Planning to be come one}
%    \end{choicequestion}

%    \begin{choicequestion}[cols=6]{What is our occupation?}
%      \ExplSyntaxOn
%      \sdaps_context_set:n {checkbox={ellipse}}
%      \ExplSyntaxOff
%      \choiceitem{Student}
%      \choicemulticolitem{2}{Software development}
%      \choiceitemtext{1.2cm}{3}{Other:}
%    \end{choicequestion}


    \section{General}

    \begin{markgroup}{Please rate the workshop overall}
      \markline{Was the workshop well prepared?}{very well}{not at all}
      \markline{Was the workshop well structured?}{very well}{not at all}
    \end{markgroup}

    \begin{markgroup}{Performance of the instructor}
      \markline{Was the instructor motivated?}{very motivated}{not motivated}
      \markline{How well did the instructor respond to questions?}{very well}{really bad}
      %\markline{Did the instructor keep eye contact?}{always}{never}
      \markline{Was the instructor easy to understand?}{always}{never}
      \markline{Was the instructor prepared?}{very well}{really bad}
    \end{markgroup}

    \begin{markgroup}{If applicable, please rate the hands on sessions}
      \markline{Were they well prepared?}{very well}{not at all}
      \markline{How detailed were the provided guides?}{too detailed}{too imprecise}
      \markline{Were the tutors able to help you if you got stuck?}{always}{never}
      \markline{Was the complexity appropriate for your experience?}{too complex}{too easy}
      \markline{Were the tasks at a reasonable pace for you?}{too quickly}{too slowly}
    \end{markgroup}


    \textbox*{4cm}{Please comment on the hands on sessions (e.g. good parts, bad parts, possible improvements)}

    \section{Materials}

    \begin{choicequestion}[cols=3]{What materials were used during the workshop?}
      \choiceitem{Slides}
      \choiceitem{Handouts}
      \choiceitem{Blackboard}
      \choiceitem{Online Documentation}
      \choiceitem{Prepared project files}
      \choiceitemtext{1.2cm}{1}{Other}
    \end{choicequestion}
    \begin{markgroup}{Please rate the slides (if applicable)}
      \markline{Were the slides detailed enough?}{absolutely}{not at all}
      \markline{Were the slides easy to understand?}{very easy}{not at all}
      \markline{Were the slides well structured?}{very well}{not at all}
      \markline{Were the slides well integrated into the workshop?}{very well}{not at all}
    \end{markgroup}

    \begin{markgroup}{Please rate other workshop material (if applicable)}
      \markline{Were the handouts detailed enough?}{absolutely}{not at all}
      \markline{Were the handouts easy to understand?}{very easy}{not at all}
      \markline{Were the handouts well structured?}{very well}{not at all}
      \markline{Were the handouts well integrated into the workshop?}{very well}{not at all}
    \end{markgroup}
    \textbox*{3cm}{Please comment on the material (e.g. good parts, bad parts, possible improvements)}

    \section{Overall impression}

    \singlemark{Did you enjoy this workshop}{very much}{not at all}

    \singlemark{Would you recommend this workshops to others?}{absolutely}{never}

    \singlemark{How do you rate the workshop organization (by the GUADEC team)?}{excellent}{poor}

    \textbox*{6cm}{Do you have any other comments?}

    \singlemark{Do you think that workshops at GUADEC are a good idea?}{absolutely}{not at all}


%    * Hands on
%    * Preparation of Tutors
%    * Required preparation for Workshop
%    * Struktur


%    * Beurteilung nach:
%      - Niveau
%      - Umfang
%      - Tempo
%      - ?
%    * Materialien (Folien/Blackboard/…)
%      - ausführlich genug
%      - verständlich
%      - strukturiert
%      - zur wiederholung geeignet

%    * Gesamtnote

%    * Dozent
%      - engagiert/motiviert
%      - beantwortet fragen
%      - theorie/praxis?
%      - blickkontakt
%      - vorbereitung?
%      - "wird wesentliches herausgearbeitet"
%      - Darbietung insgesamt



  \end{questionnaire}

\end{document}

